\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-02-07 tex/introduction.tex
uncomment inline figures

% \begin{figure*}[!ht]
% \centering
% \noindent\includegraphics[width=0.8\textwidth]{fig/biomodelexamples.pdf}
% \caption{{\bf Dynamical models in systems biology.} The top row represents a chemical reaction network (CRN) \cite{Shinar2010}, a gene regulatory network (GRN) \cite{Karlebach2008}, and an ecological regulatory network (ERN) \cite{Rohr2014} in terms of the graphical methods specific to each field mapped into the interaction graph, which provides a unified representation for networks across these fields. The second row represents a particular example of a system of differential equations that are used to model a biological network within each of the domains of application considered here. The third row shows the general form of a system of differential equations that can be used to model any network architecture within each domain.}
% \label{fig:biomodelexamples}
% \end{figure*}

>>>>

\begin{figure*}[!ht]
\centering
\noindent\includegraphics[width=0.8\textwidth]{fig/biomodelexamples.pdf}
\caption{{\bf Dynamical models in systems biology.} The top row represents a chemical reaction network (CRN) \cite{Shinar2010}, a gene regulatory network (GRN) \cite{Karlebach2008}, and an ecological regulatory network (ERN) \cite{Rohr2014} in terms of the graphical methods specific to each field mapped into the interaction graph, which provides a unified representation for networks across these fields. The second row represents a particular example of a system of differential equations that are used to model a biological network within each of the domains of application considered here. The third row shows the general form of a system of differential equations that can be used to model any network architecture within each domain.}
\label{fig:biomodelexamples}
\end{figure*}
